Distributions

### 2022-01-10 Ch2_distributions/Ch2_Figures.Rmd
Figures for angles are done. NEed captions now.

# Figure X - angles

```{r fig.width=8, fig.height=6}
p1_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

@@

@@

>>>>

# Figure 5 - angles

```{r Figure5, fig.width=8, fig.height=6}
p1_angles <- ptpl %>% 
  drop_na(rel.angle) %>% 
  mutate(d.angle = ifelse(rel.angle > 0, rel.angle * 180/pi,
                          rel.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

@@

ggsave("Ch2_distributions/Figures/Figure5.png")

@@

```{r}

# Relative angle requires at least three consecutive observations since it is looking at changes in direction. Whereas, the absolute angle is just the direction of movement based on the absolute plane, and thus it only requires two consecutive observations. 
ptpl %>% 
  ungroup() %>% 
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  dplyr::select(individual, sgroup, rel.angle, abs.angle) -> angles_df
```

```{r eval = FALSE}
p1_angles <- angles_df %>% 
  drop_na(abs.angle) %>% 
  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
                          abs.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  labs(title = "Complete pooling")

p2_angles <- angles_df %>% 
  drop_na(abs.angle) %>% 
  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
                          abs.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~sgroup, nrow = 2) +
  theme(axis.text = element_blank()) +
  labs(title = "Partial pooling")

p3_angles <- angles_df %>% 
  drop_na(abs.angle) %>% 
  mutate(d.angle = ifelse(abs.angle > 0, abs.angle * 180/pi,
                          abs.angle * 180/pi + 360)) %>% 
  ggplot(., aes(x = d.angle)) +
  geom_histogram(color = "grey", fill = "grey") +
  coord_polar(theta = "x", start = -pi/2, direction = -1) +
  scale_x_continuous(breaks = seq(0, 360, 30), limits = c(0, 360)) +
  theme_minimal() +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        legend.position = "none") +
  facet_wrap(~ individual, nrow = 2) +
  theme(axis.text = element_blank()) +
  labs(title = "No pooling")

plot_grid(plot_grid(p1_angles, p2_angles), p3_angles, nrow = 2)
```

```{r}

library(CircStats)

ptpl %>%
  drop_na(rel.angle) %>% 
  group_by(Bird_ID) %>%
  add_tally() %>%
  filter(n >= 30)  %>% 
  mutate(individual = paste0("B", Bird_ID),
         individual = factor(individual, levels = c("B1", "B3", "B5", "B7", "B13", "B19", "B22", "B28", "B49", "B84", "B30", "B29"))) %>% 
  dplyr::select(individual, sgroup, rel.angle, abs.angle) %>%
  drop_na(individual, rel.angle) -> angles_df

# Estimate for complete pooling

mu0 <- circ.mean(angles_df$rel.angle)
rho0 <- est.rho(angles_df$rel.angle)
angle.params <- as.data.frame(wrpcauchy.ml(angles_df$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
  mutate(model = "CP",
         group = NA)

# Partial pooling

sgroups <- paste0("G", 1:7)

for(i in 1:7){

  sub_data <- angles_df %>%
    drop_na(rel.angle) %>%
    filter(., sgroup == sgroups[i])

  mu0 <- circ.mean(sub_data$rel.angle)
  rho0 <- est.rho(sub_data$rel.angle)
  a <- as.data.frame(wrpcauchy.ml(sub_data$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
    mutate(model = "PP",
           group = sgroups[i])

  angle.params <- rbind.data.frame(angle.params, a)

}

# No pooling

individuals <- unique(angles_df$individual)

for(i in 1:12){

  sub_data <- angles_df %>%
    drop_na(rel.angle) %>%
    filter(., individual == individuals[i])

  mu0 <- circ.mean(sub_data$rel.angle)
  rho0 <- est.rho(sub_data$rel.angle)
  a <- as.data.frame(wrpcauchy.ml(sub_data$rel.angle, mu0 = mu0, rho0 = rho0)) %>%
    mutate(model = "NP",
           group = individuals[i])

  angle.params <- rbind.data.frame(angle.params, a)

}

```{r Figure6, fig.width=6, fig.height=3}
cp.mu <- angle.params$mu[which(angle.params$model=="CP")]
cp.rho <- angle.params$rho[which(angle.params$model=="CP")]

angle.params %>% 
  mutate(id = ifelse(str_detect(group, "B"), str_replace(group, "B", ""), group),
         id = case_when(
    id %in% c(1,3,5) ~ "G1",
    id %in% c(7) ~ "G2",
    id %in% c(13, 19) ~ "G3",
    id %in% c(22) ~ "G4",
    id %in% c(28) ~ "G5",
    id %in% c(49, 84) ~ "G6",
    id %in% c(29, 30) ~ "G7",
    str_detect(id, "G") ~ id
  ),
  id = as.factor(id)) -> angle.params

angle.params %>% 
  filter(., model != "CP") %>% 
  ggplot(., aes(x = model, y = mu)) +
  geom_boxplot() +
  geom_jitter(width = 0.1, aes(color = id)) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  geom_hline(yintercept = cp.mu, color = my.cols1[4], size = 1) +
  labs(x = "Pooling scenario") +
  theme_classic() +
  theme(legend.position = "none") -> muplot

angle.params %>% 
  filter(., model != "CP") %>% 
  ggplot(., aes(x = model, y = rho)) +
  geom_boxplot() +
  geom_jitter(width = 0.1, aes(color = id)) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  geom_hline(yintercept = cp.rho, color = my.cols1[4], size = 1) +
  labs(x = "Pooling scenario") +
  theme_classic() +
  theme(legend.position = "none") -> rhoplot

cir.legend <- get_legend(angle.params %>% 
  filter(., model != "CP") %>% 
  ggplot(., aes(x = model, y = rho)) +
  geom_boxplot() +
  geom_jitter(width = 0.1, aes(color = id)) +
  scale_color_manual(values=sgroup_col, drop=FALSE) +
  guides(color = guide_legend(title = "Social \n group")) +
  geom_hline(yintercept = cp.rho, color = my.cols1[4], size = 1) +
  labs(x = "Pooling scenario") +
  theme_classic())

A <- plot_grid(muplot, rhoplot, nrow = 1, labels = c("A)", "B)"), label_size = 10)
plot_grid(A, cir.legend, nrow = 1, rel_widths = c(1, 0.1))

ggsave("Ch2_distributions/Figures/Figure6.png")
```
